Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
fine tuning

%Autors: Peter Ansell1, Robert Furbank2, Kutila Gunasekera1, Jianming Guo2, David Benn3, Gareth Williams3, Xavier Sirault2
\author{Peter Ansell\inst{1}, Robert Furbank\inst{2}, Kutila Gunasekera\inst{1}, Jianming Guo\inst{2}, David Benn\inst{3}, Gareth Williams\inst{3}, Xavier Sirault\inst{2}}

@@

%\keywords{eResearch, Semantic Web, RDF, OWL, Data collection citation, BagIt, Data Access Portal}

@@

PlantScan\textsuperscript{\texttrademark} is a medium throughput high resolution phenotyping platform, which
brings together a number of imaging sensors (Light detection and ranging, Far
infrared imaging, multi-wavelength imaging) to non-invasively measure plant
growth and function using in-silico approaches [REF?]. Raw data is captured with
its contextual information (e.g. system configuration, time of acquisition,
batch number and project) and is stored in a purpose-built database as the data
is being generated. The various data streams are collated and used to produce
full 3D representation of each plant with overlaid spectral information. The
metadata collected during image acquisition are necessary inputs for the
computer vision techniques which are used to create the 3D representation of the
plant (Figure 3)[e]. The 3D meshes are then automatically segmented in order to
semantically identify the different parts of the plants (Paproki et al, 2012). A
longitudinal 3D matching pipeline for plant mesh parts is then used to evaluate 
temporal changes at the whole plant and/or organ level. After initial
processing, i.e. 3D reconstruction, the raw data for each plant is packaged into
one location using BagIt, an hierarchical file [6]. All bags belonging to the
same specific PODD project are grouped into collections on the CSIRO Data Access
Portal. These bags have a permanent address which is recorded into PODD. Any
additional processes on these digital objects (such as statistical information
on features like plant colour, volume,  growth etc. and on elements such as
petiole, stem, leaf) are also captured by PODD (Figure 1). Metadata
Each acquisition on PlantScan\textsuperscript{\texttrademark} includes metadata (in addition to the raw data
streams), such as plant genus and species, project and experiment metadata, a
unique identifier for each image (Globally Unique Identifier), imaging angle,
environmental temperature of the imaging chamber, location of optical and colour
calibration datasets for each acquisition run, LiDAR (Light Detection and
Ranging Sensors) calibration files. The metadata associated with each
acquisition is automatically generated when setting up the configuration on the
platform. This information is paramount to validate and process the raw image
data, and for the post-processing phases. This information currently resides in
the PlantScan\textsuperscript{\texttrademark} database.

>>>>

%Autors: Peter Ansell1, Robert Furbank2, Kutila Gunasekera1, Jianming Guo2,
%David Benn3, Gareth Williams3, Xavier Sirault2
\author{Peter Ansell\inst{1}, Robert Furbank\inst{2}, Kutila Gunasekera\inst{1},
Jianming Guo\inst{2}, David Benn\inst{3}, Gareth Williams\inst{3}, Xavier
Sirault\inst{2}}

@@

%\keywords{eResearch, Semantic Web, RDF, OWL, Data collection citation, BagIt,
% Data Access Portal}

@@

PlantScan\textsuperscript{\texttrademark} is a medium throughput high resolution
phenotyping platform, which brings together a number of imaging sensors--light 
detection and ranging, far-infrared imaging, and multi-wavelength imaging--to non-invasively measure plant growth and function using in-silico approaches.
% FIXME: TODO: [REF?] for PlantScan. 
Raw data is captured with
its contextual information (e.g. system configuration, time of acquisition,
batch number and project) and is stored in a purpose-built database as the data
is being generated. The various data streams are collated and used to produce
full 3D representation of each plant with overlaid spectral information. The
metadata collected during image acquisition are necessary inputs for the
computer vision techniques which are used to create the 3D representation of the
plant (Figure 3)[e]. The 3D meshes are then automatically segmented in order to
semantically identify the different parts of the plants (Paproki et al, 2012). A
longitudinal 3D matching pipeline for plant mesh parts is then used to evaluate 
temporal changes at the whole plant and/or organ level. After initial
processing, i.e. 3D reconstruction, the raw data for each plant is packaged into
one location using BagIt, an hierarchical file [6]. All bags belonging to the
same specific PODD project are grouped into collections on the CSIRO Data Access
Portal. These bags have a permanent address which is recorded into PODD. Any
additional processes on these digital objects (such as statistical information
on features like plant colour, volume,  growth etc. and on elements such as
petiole, stem, leaf) are also captured by PODD (Figure 1). Metadata
Each acquisition on PlantScan\textsuperscript{\texttrademark} includes metadata
(in addition to the raw data
streams), such as plant genus and species, project and experiment metadata, a
unique identifier for each image (Globally Unique Identifier), imaging angle,
environmental temperature of the imaging chamber, location of optical and colour
calibration datasets for each acquisition run, LiDAR (Light Detection and
Ranging Sensors) calibration files. The metadata associated with each
acquisition is automatically generated when setting up the configuration on the
platform. This information is paramount to validate and process the raw image
data, and for the post-processing phases. This information currently resides in
the PlantScan\textsuperscript{\texttrademark} database.
